%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects, Publications \& Courses}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}


%---------------------------------------------------------

     \cventry
    {Development Proficiency } % Role
    {Termetris} % Event
    {IIT Roorkee} % Location
    {Jan. 2019 - Apr. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s)}
        \item {Termetris is a terminal based game of tetris, written in C using curses library.}
        \item {https://github.com/frederick99/termetris}
      \end{cvitems}
    } 

%---------------------------------------------------------
  \cventry
    {Database Management Systems course} % Role
    {Relational Database Implementation for Facebook} % Event
    {IIT Roorkee} % Location
    {Jul. 2018 - Nov. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s)}
        \item {Created Entity-relationship and schema diagram}
        \item {Normalized the tables and discovered covers.}
        \item { Implemented in MySQL, along with queries for supporting basic features.}
      \end{cvitems}
    }

%---------------------------------------------------------
 \cventry
    {Operating Systems course} % Role
    {Kernel Lottery Scheduler} % Event
    {IIT Roorkee} % Location
    {Jan. 2018 - Apr. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s)}
        \item {Implemented Lottery Scheduling policy in xv6 kernel.}
        \item {Remodelled the process structure of the kernel.}
        \item {Added system calls for ticket Inflation and to capture the working of the scheduler.}
      \end{cvitems}
    }

%---------------------------------------------------------

% SIC/XE Assembler | IIT-Roorkee	Jan 18 - April 18
%     • Developed an Two-pass Assembler with multiple addressing modes in C++.
%     • Added support for error logging, Modification records.

 \cventry
    {System Software course} % Role
    {SIC/XE Assembler} % Event
    {IIT Roorkee} % Location
    {Jan. 2018 - Apr. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s)}
        \item {Developed an Two-pass Assembler with multiple addressing modes in C++.}
        \item {Added support for error logging, Modification records}
      \end{cvitems}
    }

%---------------------------------------------------------
     \cventry
    {Lab Project} % Role
    {Face Generation - thispersondoesnotexist.com implementation} % Event
    {IIT Roorkee} % Location
    {Jan. 2019 - Apr. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s)}
        \item {Generated random human faces using GAN and autoencoders.}
        \item {Added the ability to alter learned features.t}
      \end{cvitems}
    }    

\end{cventries}
